---
title: "Data Jobs in the U.S. Government"
author: "Andrew C"
date: "11/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overview

The goal of this project is to answer the business question: How to become a Data Analyst in the U.S. government?
Therefore, this document showcases the requirements for data-related job fields with the U.S. Government. This data is collated from the Office of Personnel Management (OPM) and the USAJobs.gov API. **The project is broken down into the following steps**

### Step 1: Extract Data
For this project, I extracted live data (or Requested it) using API calls with the USAJobs.gov Rest API. This process was worth it, as this source has clean, publicly available data.

### Step 2: Transfer Data from JSON file to Daily CSV file

* Writing a separate script to run the the transfer

### Step 3: Automate Entire Process

* Run Cron Job to run script automatically at set time for 1 week 

### Step 4: Clean Data
* Automate SQL and Data cleaning functions. 

### Step 5: Visualize Data 
* Take data and create visuals. Automate if possible. 

### Step 6: Insights Overview
* Provide overview of insights. 

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



